\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc} % Включаем поддержку UTF8  
\usepackage[russian]{babel}  % Включаем пакет для поддержки русского языка  
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large ILYA SHIRKO} & Email : \href{mailto:ilyashirko@gmail.com}{ilyashirko@gmail.com}\\
  \textbf{\Large Middle PYTHON developer} & Mobile : \href{tel:+79112640455}{+7 911 264-04-55} \\
\end{tabular*}


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Technologies}{: Flask, Django, DRF, PostgreSQL, Redis, Kubernetes, Docker, Prometheus, ArgoCD, Grafana, Yandex Cloud, Linux, Bootstrap, HTML/CSS}
   }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rebrain}{Russia, Moscow (remote)}
      {Middle Python Developer}{Jun 2023 - Present}
      \resumeItemListStart

        \resumeItem{Infrastructure}
          {(Flask, Kubernetes, Docker, YandexCloud, AWS, DigitalOcean, CloudFlare)}\\
          {Developed infrastructure for creating groups of virtual machines and executing various scripts.}\\

        \resumeItem{Support}
          {(ArgoCD, kubectl, docker CLI, YandexCloud CLI, Prometheus, Grafana)}\\
          {Helped with backend support. Explored issues on VMs.}

        \resumeItem{AD-HOC}
          {(Flask, FFMPEG, Amo CRM, Zoom API, Telegram API)}\\
          {Integrations with third party services, video processing with GPU acceleration. Code-review.}
        
        \resumeItem{CI/CD}
          {(GitLab, Kubernetes, Docker, ArgoCD)}\\
          {Deployment services on kubernetes with GitLab CI/CD, ArgoCD, wrote YAML manifests.}
        
        \resumeItem{Database}
          {(PostgreSQL, SQLAlchemy, alembic)}\\
          {Raw SQL DB processing, database design for new services}

      \resumeItemListEnd

    \resumeSubheading
      {Devman}{Russia, Moscow (remote)}
      {Pre-middle Python Developer}{Jan 2022 - Jun 2023}
      \resumeItemListStart

        \resumeItem{Freelance exchange}
          {(Django, Redis, Telegram API)}\\
          {Implemented bot logic, refactored the DB architecture, reviewed the code of the co-developers. \href{https://github.com/ilyashirko/osminog}{\textit{see on GitHub}}}

        \resumeItem{Pizza telegram store}
          {(Redis, Telegram API, Motlin API) }\\
          {Telegram-based online store for pizzeria chain. \href{https://github.com/ilyashirko/pizza-shop}{\textit{see on GitHub}}}

        \resumeItem{Burgers online store}
          {(Django, DRF, geopy, PostgreSQL, Docker)}\\
          {Full backend, set up frontend and backend, authorization, deployment. \href{https://github.com/ilyashirko/burger_store}{\textit{see on GitHub}}}

        % \resumeItem{FAQ support chat-bot}
        %   {(Google Cloud (DialogFlow), VK API, Telegram API)}\\
        %   {Full-stack development. \href{https://github.com/ilyashirko/verb_games_support_bot}{\textit{see on GitHub}}}

        \resumeItem{Interactive map generator}
          {Django, HTML/CSS}\\
          {Full backend, set up frontend and backend, deployment. \href{https://github.com/ilyashirko/city_guide}{\textit{see on GitHub}}}

      \resumeItemListEnd

    \resumeSubheading
      {Self-employment}{Russia, Saint-Petersburg}
      {Software Engineer}{}
      \resumeItemListStart

        \resumeItem{YES Code studio}
          {(Django, HTML/CSS, Bootstrap 5, Telegram API)} \\
          {Site and telegram bot for software startup.}

        \resumeItem{ServiceCenter CRM}
          {(Django, DRF, Telegram API)} \\
          {Lite version of CRM system for service center orders based on Telegram API. \href{https://github.com/ilyashirko/service_center}{\textit{see on GitHub}}}

        \resumeItem{Inventory app for tile warehouse}
          {(Django, Redis, Pandas, Telegram API)}\\
          {Service for controlling balances and movement of goods based on Telegram API.}

			\resumeItemListEnd
    
      \resumeSubheading
      {XCase, ООО Эльдорадо, ГК Хорошая связь, ПАО Вымпелком, ...}{Russia, Saint-Petersburg}
      {Sales office director, Sales coach, Sales manager}{2011 - 2022}
      \resumeItemListStart
        \resumeItem{Total experience}
          {The total experience, taking into account breaks, was about 8 years.}
        \resumeItem{Awards}
          {Best results for the quarter. (ГК Хорошая связь)}
        \resumeItem{Main responsibilities}
          {Training and control of personnel, sale, adjustment and repair of portable electronics. Interaction with the central office and controlling organizations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{PET projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Mass mailing service}
      {(Python 2.7, Django 1.11, Celery, Redis, Gmail). Full-stack development. \href{https://github.com/ilyashirko/mailganer}{\textit{see on GitHub}}}
    \resumeSubItem{Football matches daily parser}
      {(Selenium, BS4, SQL) Full-stack development. \href{https://github.com/ilyashirko/fs_selenium}{\textit{see on GitHub}}}

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DVMN.org}{2022 -- 2023}
      {Django, HTML/CSS, API, Django ORM, Advanced layout, Chat-bots, Docker, Async, Git, Code review}{}
    \resumeSubheading
      {SYNERGY univercity}{2018 -- 2023}
      {Bachelor of Civil Jurisprudence}{}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}


